Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-16 tex/ms.tex
note that gaussian for absorption lines is not a very good model

BDJ IMPROVE DISCUSSION OF BROADENING.  The model spectra are smoothed
by convolution with a Gaussian in wavelength space (to model the MMT
line-spread function) and are interpolated to the wavelength points of
the of the observed spectrum while taking into account the
redshift. The instrumental resolution is given by $\sigma$.  Discuss
Intrinsic resolution of model spectra (MILES), whether instrumentasl
resolution is larger, smaller, or comparable to intrinsic velocity
broadening.

Nebular emission lines (which may arise from HII regions around the
clusters or from diffuse ionized gas) and interstellar absorption
lines are modeled as a sum of Gaussians of unknown amplitude $A_\ell$,
all of the same width $\sigma_e$ (which need not be the same as
stellar broadening $\sigma$) and with known central wavelengths
$\lambda_\ell$.  For emission lines the amplitudes are constrained to be
positive, while for interstellar absorption (e.g. Na D and Ca K) the
amplitudes are constrained to be negative. This framework can be
easily extended to include more complex models for the nebular
emission, such as allowing line dependent widths and velocities.

@@

BDJ INSERT WORDS HERE.  We have demonstrated that we can combine
photometric and spectroscopic data in a principled way to infer
physical properties.  We do not resort to an arbitrary down-weighting
or up-weighting of certain data. Instead, we explicitly model our
uncertain knowledge of the spectral calibration.  For a number of
applications this combination of spectroscopy and photometry reduces
the need for spectrophotometric calibration.  Calibration information,
if it exists, can be used to generate informative priors on the
calibration parameters of our model. Furthermore, our strategy is
easily extensible to more complicated models, which include for
example night sky line emission in the spectroscopy, wavelength
calibration.

In a heirarchical model it should be possible to use the inferred
calibration parameters, along with additional information about the
observations (e.g. airmass, instrument temperature), to in turn infer
the parameters of a generative model for the calibration.

Limitations.  The strategy we have outlined here has several
limitations.  First, it requires a generative model for the spectrum of
the object of interest, and is thus ill-suited to discovery projects.

>>>>

BDJ IMPROVE DISCUSSION OF BROADENING.  The model spectra are smoothed
by convolution with a Gaussian in wavelength space (to model the MMT
line-spread function) and are interpolated to the wavelength points of
the of the observed spectrum while taking into account the
redshift. The instrumental resolution is given by $\sigma$.  Discuss
intrinsic resolution of model spectra (MILES), what to do in
situations where instrumental resolution is higher, lower or
comparable (ouch) to intrinsic velocity broadening.

Nebular emission lines (which may arise from HII regions around the
clusters or from diffuse ionized gas) and interstellar absorption
lines are modeled as a sum of Gaussians of unknown amplitude $A_\ell$,
all of the same width $\sigma_e$ (which need not be the same as
stellar broadening $\sigma$) and with known central wavelengths
$\lambda_\ell$.  For emission lines the amplitudes are constrained to
be positive, while for interstellar absorption (e.g. Na D and Ca K)
the amplitudes are constrained to be negative. This framework can be
easily extended to include more complex models for the nebular
emission, such as allowing line dependent widths and velocities, and
using Voight profiles for the line shapes.  NB GAUSSIANS ARE A NOT
GREAT APPROXIMATION FOR ABSORPTION LINE SHAPES (GAUSSIAN IN OPTICAL
DEPTH, NOT $\Delta F$)

@@

BDJ INSERT WORDS HERE.  We have demonstrated, using a sample of
stellar clusters in M31, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly model our uncertain knowledge of
the spectral calibration and infer it along with the physical
properties. For a number of applications this combination of
spectroscopy and photometry reduces the need for spectrophotometric
calibration.  Calibration information, if it exists, can be
incorporated into informative priors on the calibration parameters of
our model.

Our strategy is easily extensible to more complicated models, which
include for example night sky line emission in the spectroscopy,
wavelength calibration.  DISCUSS MORE COMPLICATED COVARIANCE KERNELS,
MULTIPLE KERNELS, etc.  MODEL CHECKING.

In a heirarchical modelling context it should be possible to use the
inferred calibration parameters, along with additional information
about the observations (e.g. airmass, instrument temperature), to in
turn infer the parameters of a generative model for the
calibration. This generative model can then be used in the
(probabilistic) calibration of objects where the spectra are difficult
to model explicitly.

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model.  Third, we have made the assumption that
the spectrscopy and the photometry are sampling the same populations.
In practice, differences between spectroscopic and photometric
apertures mean that the photometry and the spectroscopy are sampling
slightly different physical regions.  The correct response to this
situation is to explicitly model the differences, incorporating prior
information about the spatial variation of physical properties.
Finally, this method is computationally intensive and expensive, since
we are constantly inverting largish matrices.
